### 2020-08-28 README.Rmd
add doi badge

@@

# The problem and promise of scale in multilayer networks
Alec Robitaille, Quinn M.R. Webber, Julie Turner and Eric Vander Wal

## TODO
```{bash}
grep -rni 'R/' -e 'TODO' || true;
grep -rni 'scripts/' -e 'TODO' || true;
grep -rni 'paper/manuscript.Rmd' -e 'TODO' || true;
```

>>>>

[![DOI](https://zenodo.org/badge/291094231.svg)](https://zenodo.org/badge/latestdoi/291094231)

@@

# The problem and promise of scale in multilayer networks

* Authors:
    + [Alec L. Robitaille](http://robitalec.ca)
    + [Quinn M.R. Webber](https://qwebber.weebly.com/)
    + [Julie W. Turner](https://www.julwturner.com/)
    + [Eric Vander Wal](http://weel.gitlab.io)
